### 2014-10-23 Docs/managing_jobs/managingjobs.tex
Flesh out the notes on Blue Waters

>>>>

\section{Working at NCSA (Blue Waters)}

\subsection{Overview}

Blue Waters consists of 22,640 Cray XE6 compute nodes and 4,224
Cray XK7 compute nodes.

Each XE node has two AMD Interlagos model 6276 compute units, each of
which has 16 integer cores (thus, a single node has a total of 32 integer
cores).  Two integer cores share a multithreaded, 256-bit wide floating 
point unit (FPU).  If both integer cores have their own thread, each has access 
to 128-bit floating point processing, whereas if only one thread is 
assigned the process can access all 256 bits.  In one major science
application on Blue Waters it was found that having an OpenMP thread for
each integer core gave the best performance, but when starting a new
application it's best to experiment.  One OpenMP thread per FPU may
be better in some cases.

Each compute unit is divided into two NUMA nodes.  Cores in
the same NUMA region share a pool of L3 cache.  For the same science
application as before it was found that the best performance was achieved
by assigning an MPI task to each NUMA node.  Thus, each physical node
has four MPI tasks.

The XK nodes consist of one AMD Interlagos model 6276 compute unit
and an NVIDIA GK110 ``Kepler'' GPU accelerator (Tesla K20X).  The
GPU is configured with 14 streaming multiprocessor units (SMXs), each
of which has 192 single-precision or 64 double-precision CUDA cores.  Thus
there are a total of 2688 SP CUDA cores or 896 DP CUDA cores.

For more details, please see 
\url{https://bluewaters.ncsa.illinois.edu/user-guide}

\subsection{BW Compilers}

The Cray compilers are the default on blue waters, and version
8.3.3 works well with \maestro.

\subsection{Monitoring Allocations}

The {\tt usage} command will list the current user's usage and 
{\tt usage -P {\em project}} will
list the usage for all users in a project allocation named ``project''.
